### 2015-09-10 vmcai-2016-tex/approach.tex
Re-worked parts of the introduction for clarity. Added transition material to sections on GSE and symbolic initialization.

\section{Generating and Updating Symbolic Heaps}
\label{sec:precise}

Unlike~\gsetxt{}, the symbolic heap algorithm only partitions the heap at comparison
operations or for exception handling.  There are three sets of rewrite
rules specific to the symbolic heap algorithm: (i) rules to initialize
symbolic references, (ii) rules to perform field dereferences and
writes, and (iii) rules to check equality and inequality of
references.

>>>>

\section{Symbolic Initialization}
\label{sec:precise}
Although the case-splitting methods used in~\gsetxt{} can be applied
to guarded value sets, a direct implementation would run into the same
path explosion problems. This work presents a new initialization scheme which avoids the
nondeterminism introduced by~\gsetxt{}. Called \emph{\symtxt{}}, this scheme leverages the core idea in generalized symbolic execution
with lazy initialization, using on-the-fly reasoning to model a
black-box input heap during symbolic execution. Unlike~\gsetxt{}, \symtxt{} constructs a single
symbolic heap and polynomially-sized path condition for each control
flow path.

There are three sets of rewrite
rules specific to the~\symtxt{} algorithm: (i) rules to initialize
symbolic references, (ii) rules to perform field dereferences and
writes, and (iii) rules to check equality and inequality of
references.

### 2015-09-10 vmcai-2016-tex/intro.tex
Re-worked parts of the introduction for clarity. Added transition material to sections on GSE and symbolic initialization.

A common hurdle to using guarded value sets is the treatment of symbolic heap inputs. Precisely modeling operations on heap inputs is challenging because it requires formulating logical predicates over an input domain that contains a potentially unbounded number of references~\cite{Chen:2013,Qu:2011}. Manually creating test inputs can be a time consuming and error-prone process, automatic case-splitting methods~\cite{GSE03,Deng:2007} quickly produce an overwhelming number of execution paths, and user-supplied logical invariants require a high degree of skill to create. Thus, despite the advantages of using guarded value sets, it remains an open question how they can be used in symbolic execution to automatically model all possible program behaviors in the case of an arbitrary input heap.

>>>>

A common hurdle to using guarded value sets is the treatment of symbolic heap inputs. For many applications, it is desirable to model the input heap as a black box, with operations over the input references providing the only means of divining its structure. Precisely modeling operations on black-box heap inputs is challenging because it requires formulating logical predicates over an input domain that contains a potentially unbounded number of hidden references~\cite{Chen:2013,Qu:2011}. Generalized symbolic execution (\gsetxt{}) methods~\cite{GSE03,Deng:2007} provide an accurate solution, but they quickly produce an overwhelming number of execution paths for all but the simplest heap shapes. Efforts to extend~\gsetxt{} principles to guarded value sets have failed to produce provably equivalent results. Thus, despite the advantages of using guarded value sets, it remains an open question how they can be used in symbolic execution to automatically model all possible program behaviors in the case of an arbitrary input heap.

### 2015-09-10 vmcai-2016-tex/lazy.tex
Re-worked parts of the introduction for clarity. Added transition material to sections on GSE and symbolic initialization.

\subsection{Generalized Symbolic Execution}
\label{app:gse}
The rules to generalized symbolic execution with
lazy initialization using the symbolic heap are in
\figref{fig:lazyInit} for the initialization and \figref{fig:lazy} for
how the initialization is used. Specifically, the field-access rule in
\figref{fig:lazy} uses initialization, $\rightarrow_I^*$, to ensure
the accessed field is instantiated. Initialization in generalized
symbolic execution never happens for more than one object on any use
of $\rightarrow_I^*$: $\Lambda$ is either empty or contains exactly
one location.

>>>>

\subsection{Generalized Symbolic Execution}
\label{app:gse}
Several projects have generalized the core idea of symbolic execution,
enabling it to be applied to programs with more general types,
including references and
arrays~\cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}. These
generalized symbolic execution (\gsetxt{}) techniques work by branching over
multiple copies of the system state during dereferencing operations, creating
new location symbols on an as-needed basis in a process called~\emph{lazy initialization}.

The rules to generalized symbolic execution with
lazy initialization using the symbolic heap are in
\figref{fig:lazyInit} for the initialization and \figref{fig:lazy} for
how the initialization is used. Specifically, the field-access rule in
\figref{fig:lazy} uses initialization, $\rightarrow_I^*$, to ensure
the accessed field is instantiated. Initialization in generalized
symbolic execution never happens for more than one object on any use
of $\rightarrow_I^*$: $\Lambda$ is either empty or contains exactly
one location.
